### 2016-06-24 docs/ms_communitySynchrony.Rmd
fixes small typo in ms

Theory identifies the three main determinants of species synchrony as environmental stochasticity, demographic stochasticity, and \hl{interspecific interactions} [@Loreau2008a; @Gonzalez2009; @Loreau2013].
For example, in a community composed of large (no demographic stochasticity) and weakly interacting (no interspecific \hl{interactions}) populations, community-wide species synchrony should be determined by the covariance of species' responses to the environment [@Loreau2008a].
However, such a prediction relies on a relatively simple population model and only holds under two assumptions: (i) species' responses to the environment are similar in magnitude and (ii) all species have similar growth rates.
\hl{Whether such theoretical predictions hold in natural communities where species differences are unlikely to be symmetrical remains relatively unkown because only a few studies have explicitly tested theory on the drivers of species synchrony in natural communities} [@Mutshinda2009; @Thibaut2012], \hl{and they did not consider demographic stochasiticity.}

>>>>

Theory identifies the three main determinants of species synchrony as environmental stochasticity, demographic stochasticity, and \hl{interspecific interactions} [@Loreau2008a; @Gonzalez2009; @Loreau2013].
For example, in a community composed of large (no demographic stochasticity) and weakly interacting (no interspecific \hl{interactions}) populations, community-wide species synchrony should be determined by the covariance of species' responses to the environment [@Loreau2008a].
However, such a prediction relies on a relatively simple population model and only holds under two assumptions: (i) species' responses to the environment are similar in magnitude and (ii) all species have similar growth rates.
\hl{Whether such theoretical predictions hold in natural communities where species differences are unlikely to be symmetrical remains relatively unkown because only a few studies have explicitly tested theory on the drivers of species synchrony in natural communities} [@Mutshinda2009; @Thibaut2012], \hl{and they did not consider demographic stochasticity.}
